Allee Effect and Cultural Evolution

### 2015-06-18 manuscript/draft.tex
updated reference

The last three decades have witnessed a steady growth of formal models of cultural evolution. Early works inspired by population biology \citep{cavallisforza_feldman_1981,boyd1985} have laid the foundation of a now mature trans-disciplinary field which unites the social and biological sciences \citep{mesoudi_etal_2006}. The rich cross-fertilisation between different fields has fomented the designing of new analytical techniques as well as new usage for existing methods, but more crucially have prompted the development of theoretical models of how culture is acquired and transmitted between individuals. %Add reference?

>>>>

The last three decades have witnessed a steady growth of formal models of cultural evolution. Early works inspired by population biology \citep{cavallisforza_feldman_1981,boyd1985} have laid the foundation of a now mature trans-disciplinary field which unites the social and biological sciences \citep{mesoudi_etal_2006}. The rich cross-fertilisation between different fields has fomented the designing of new analytical techniques as well as new usage for existing methods, but more crucially have prompted the development of theoretical models of how culture is acquired and transmitted between individuals~\citep{mesoudi_cultural_2015}.
